---
title: "Plotting DNA Copy Number Alterations"
author: "Scott Furlan"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
params:
  EVAL: !r identical(Sys.getenv("NOT_CRAN"), "true")
vignette: >
  %\VignetteIndexEntry{Plotting DNA Copy Number Alterations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
alias: cna_plotting_overview
editor_options: 
  chunk_output_type: console
---

```{r, child="children/SETTINGS-knitr_wide.txt"}
```

## Theory

To make a CNA plot in *pacbiowdlR*, you need two files as input both of which are output in the *pacbiowdlR* pipeline: 1) a depth file output and 2) a variant file which denotes the copy alteration ranges.

There are three different methods used to visualize the delta values in your CNA plot. In each case, let

- \( s(x) \) denote the observed score (or coverage value) at position \( x \),
- \(\delta(x)\) be the computed delta value at position \( x \).

### 1. Simple Difference ("delta" method)

In the simplest method, the delta is computed as the difference between the observed score and the mean score over all positions. Mathematically, if the mean score is

\[
\bar{s} = \frac{1}{N} \sum_{i=1}^{N} s(x_i),
\]

then the delta for a given position \( x \) is

\[
\delta(x) = s(x) - \bar{s}.
\]

This method highlights how much a given data point deviates from the overall average.

---

### 2. LOESS-Based Log-Ratio ("loess" method)

In this approach, a nonparametric regression (LOESS) is used to fit a smooth curve to the observed scores as a function of \( x \). Let the LOESS-fitted values be denoted by \(\hat{s}_{\text{LOESS}}(x)\). Then, the delta is computed as the log<sub>2</sub> ratio of the observed score to the fitted value:

\[
\delta(x) = \log_2\left(\frac{s(x)}{\hat{s}_{\text{LOESS}}(x)}\right).
\]

This transformation emphasizes relative differences rather than absolute differences. Using the log ratio, you capture percentage-like changes in coverage relative to the locally expected value.

---

### 3. Linear Model Fit-Based Log-Ratio ("fit" method) -- PREFERRED

For the "fit" method, a linear regression model is used to predict the coverage score based on predictors such as GC content and repeat fraction. Suppose the model is given by

\[
s(x) = \beta_0 + \beta_1 \cdot \text{gc\_content}(x) + \beta_2 \cdot \text{repeat\_fraction}(x) + \varepsilon,
\]

and let \(\hat{s}_{\text{fit}}(x)\) be the predicted (fitted) value from this linear model. Then, the delta is defined in the same way as for the LOESS method but using the fitted score:

\[
\delta(x) = \log_2\left(\frac{s(x)}{\hat{s}_{\text{fit}}(x)}\right).
\]

Here, the log<sub>2</sub> ratio provides a measure of how the observed score deviates from what is expected based on the linear relationship with GC content and repeat fraction.


Each method has its own advantage: the simple difference is easy to compute and interpret, while the log-ratio methods ("loess" and "fit") provide a relative measure that can stabilize variance and better highlight proportional changes across the genome.  The "loess" method is significantly slower, so we plot the other two here.  The delta method produces a wider range of values, so we recommend not constraining the plot dimensions.  Otherwise the dimensions can be specified as below.




```{r, fig.width=15, fig.height=3, out.width="100%", fig.asp=0.2, eval=TRUE}
library(pacbiowdlR)
depth_file <- system.file("extdata", "examples/K562.GRCh38.hificnv.depth.bw", package = "pacbiowdlR")
cna_calls <- system.file("extdata", "examples/K562.GRCh38.hificnv.vcf.gz", package = "pacbiowdlR")

CNA_plot(depth_bigwig_file  =   depth_file, trend_regions = "inside",
  variant_file       =   cna_calls, 
  downsample         = 0.1,  method = "delta",
  samplename         = "K562")

CNA_plot(depth_bigwig_file  =   depth_file,
  variant_file       =   cna_calls, method = "fit", 
  samplename         = "K562", max_value = 3, min_value = -3)

```

## Some plotting aesthetics

In the below we define some colors and replot.  Using these colors a black-colored fit line looks best

```{r, fig.width=15, out.width="200%", eval=TRUE}
chrom_palette <- c(
  "#FF0000", "#FF9900", "#FFCC00", "#00FF00", "#6699FF", "#CC33FF",
  "#999912", "#999999", "#FF00CC", "#CC0000", "#FFCCCC", "#FFFF00",
  "#CCFF00", "#358000", "#0000CC", "#99CCFF", "#00FFFF", "#ECFFFF",
  "#9900CC", "#CC99FF", "#996600", "#666600", "#666666", "#CCCCCC",
  "#79CC3B", "#E0EC3B", "#CCC99F"
)

CNA_plot(depth_bigwig_file  =   depth_file,
  variant_file       =   cna_calls,
  method = "fit", line_color = "black",
  samplename         = "K562", max_value = 3, min_value = -3, colors = chrom_palette)


```


By default, CNA_plot will "accentuate" copy number changes in deleted or duplicated regions by applying a weight to those regions outside of variants.  This effectively minimimizes the visualized variance in these regions.  This feature can be turned off, or modulated by adjusting the weight via the `outside_weight` parameter.  One can also change the weighting of the `inside_weight` to further maximize visualization.  However it is critical to note that these weights are applied AFTER estimating the y-axis values, therefore one should interpret the values with caution.

```{r, fig.width=15, out.width="200%", eval=TRUE}

CNA_plot(depth_bigwig_file  =   depth_file,
  variant_file       =   cna_calls, outside_weight = 0.4, inside_weight = 2,
  method = "fit", line_color = "black", max_value = 5, min_value = -5,
  samplename         = "K562", colors = chrom_palette)


```


### Deeper analysis of CNA

Using *pacbiowdlR*, one can take a deeper look at copy number alterations.  For example in Chr9 of the K562 data, we see regions of signifiantly deleted DNA (as evidenced by coverage inference).  We can use the `CNA_plot_highlight` function to discover genes amplified in this region.  Two additional objects are needed for gene highlighting, a txdb and org annotation file.


```{r, fig.width=15, out.width="200%", eval=TRUE}

CNA_plot_highlight(depth_bigwig_file  =   depth_file, 
                  txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, gene_delta_threshold = 2.5,
                  variant_file       =   cna_calls, downsample = 1,
                  method = "fit", line_color = "black", chr_filter = "chr9",
                  samplename         = "K562", colors = chrom_palette)
```

One will not that there are regions that plot as having a 0 value for DNA content.  This results when the log2 ratio is infinitely negative and are indicative of a complete loss of DNA in the region.  This can be confirmed using the `delta` method of visualization as shown below. We can increase the number of events plotted using the `downsample` parameter. Unsurprisingly the region lost contains the tumor suppressors CDKN2A, CDKN2B.

```{r, fig.width=15, out.width="200%", eval=TRUE}
CNA_plot_highlight(depth_bigwig_file  =   depth_file, 
                  txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, downsample = 1,
                  variant_file       =   cna_calls, max_value = 20,
                  method = "delta", line_color = "black", chr_filter = "chr9", highlight_genes = c("CDKN2A", "CDKN2B"), 
                  samplename         = "K562", colors = chrom_palette)
```

Looking at allele frequencies.  The HifiCNV program also outputs

```{r}
f<-"/Volumes/furlan_s/sfurlan/pacbiorerun/pbWGS/K562/20250211_115553_humanwgs_singleton/call-upstream/call-hificnv/work/K562.GRCh38.hificnv.maf.bw"
f<-"/Volumes/furlan_s/sfurlan/250302_leuklong/pbWGS/LL1_S1/20250302_232026_humanwgs_singleton/call-upstream/call-hificnv/work/LL1_S1.GRCh38.hificnv.maf.bw"
cna_calls <- "/Volumes/furlan_s/sfurlan/250302_leuklong/pbWGS/LL1_S1/20250302_232026_humanwgs_singleton/call-upstream/call-hificnv/work/LL1_S1.GRCh38.hificnv.vcf.gz"
p2<-MAF_plot(f, variant_file = cna_calls, downsample = 1, chr_filter = "chr9", colors = chrom_palette)
p1<-CNA_plot(depth_bigwig_file  =   depth_file, downsample = 1,
                  variant_file       =   cna_calls, max_value = 5, min_value = -5,
                  method = "fit", line_color = "black", chr_filter = "chr9",
                  colors = chrom_palette)
p1/p2

library(patchwork)

library(rtracklayer)
library(GenomeInfoDb)
library(data.table)
library(dplyr)
library(zoo)
library(ggplot2)
library(ggrepel)
```

```{r}
library(rtracklayer)
library(magrittr)
library(dplyr)
library(data.table)
library(ggplot2)
undebug(MAF_plot)
MAF_plot <- function (maf_bigwig_file, variant_file, downsample = 0.03, 
    point_size = 0.01, colors = NULL, 
    max_value = NULL, min_value = NULL, min_variant_distance = 10000, jitter_y = 0.04,
    samplename = "", chr_filter = NULL, trend_window = 50, variant_alpha = 0.1, 
    trend_regions = "inside", exclude_xy = TRUE, return_data = FALSE) 
{
    
    coverage_data <- import.bw(maf_bigwig_file)
    coverage_data <- keepStandardChromosomes(coverage_data, pruning.mode = "tidy")
    coverage_data <- as.data.frame(coverage_data)
    valid_chromosomes <- paste0("chr", c(as.character(1:22), 
        "X", "Y"))
    if (exclude_xy) {
        valid_chromosomes <- paste0("chr", as.character(1:22))
    }
    coverage_data <- coverage_data %>% filter(seqnames %in% valid_chromosomes)
    if (!is.null(chr_filter)) {
        coverage_data <- coverage_data %>% filter(seqnames == 
            chr_filter)
    }
    set.seed(42)
    sampled_indices <- sample(seq_len(nrow(coverage_data)), size = max(1, 
        floor(nrow(coverage_data) * downsample)))
    coverage_data <- coverage_data[sampled_indices, ]
    coverage_data$delta_weighted <- coverage_data$score
    vcf <- fread(variant_file, skip = "#CHROM")
    colnames(vcf)[1] <- "CHROM"
    vcf <- vcf %>% filter(CHROM %in% valid_chromosomes)
    if (!is.null(chr_filter)) {
        vcf <- vcf %>% filter(CHROM == chr_filter)
    }
    end_vals <- strsplit(vcf$INFO, ";") %>% sapply("[[", 3) %>% 
        gsub("END=", "", .) %>% as.numeric()
    type_vals <- strsplit(vcf$INFO, ";") %>% sapply("[[", 2) %>% 
        gsub("SVTYPE=", "", .)
    variant_calls <- data.frame(seqnames = vcf$CHROM, start = vcf$POS, 
        end = end_vals, type = type_vals)
    if (!is.null(min_variant_distance) && min_variant_distance > 
        0) {
        variant_calls <- variant_calls %>% mutate(distance = end - 
            start) %>% filter(distance >= min_variant_distance)
    }
    offset <- generate_offsets(coverage_data, variant_calls)
    variant_df <- offset$variant_calls
    data_highlight <- data.frame()
    if (nrow(variant_df) > 0) {
        data_highlight <- data.frame(xmin = variant_df$cumulative_start, 
            xmax = variant_df$cumulative_end, ymin = -Inf, ymax = Inf, 
            VariantType = variant_df$type, seqnames = variant_df$seqnames, 
            x_center = (variant_df$cumulative_start + variant_df$cumulative_end)/2)
    }
    offset$coverage_data <- offset$coverage_data %>% arrange(cumulative_genomic_position)
    # if (!is.null(min_value)) {
    #     offset$coverage_data$delta_weighted[offset$coverage_data$delta_weighted < 
    #         min_value] <- min_value
    # }
    # if (!is.null(max_value)) {
    #     offset$coverage_data$delta_weighted[offset$coverage_data$delta_weighted > 
    #         max_value] <- max_value
    # }
    chromosome_boundaries <- offset$coverage_data %>% group_by(seqnames) %>% 
        summarize(boundary = min(cumulative_genomic_position), 
            .groups = "drop")
    chromosome_midpoints <- offset$coverage_data %>% group_by(seqnames) %>% 
        summarize(midpoint = mean(range(cumulative_genomic_position)), 
            .groups = "drop")
    if (is.null(colors)) {
        chromosome_order <- c(as.character(1:22), "X", "Y")
        if (exclude_xy) {
            chromosome_order <- as.character(1:22)
        }
        colors <- rep(c("black", "gray"), length.out = length(chromosome_order))
        names(colors) <- paste0("chr", chromosome_order)
    }
    p <- ggplot() + geom_jitter(data = offset$coverage_data, aes(x = cumulative_genomic_position, 
        y = delta_weighted, color = seqnames), size = point_size, height=jitter_y) + 
        scale_color_manual(values = colors, drop = FALSE) + {
        if (nrow(data_highlight) > 0) {
            geom_rect(data = data_highlight, aes(xmin = xmin, 
                xmax = xmax, ymin = ymin, ymax = ymax, fill = VariantType), 
                color = "transparent", alpha = variant_alpha)
        }
        else {
            NULL
        }
    } + scale_fill_manual(values = c(DEL = "blue", DUP = "red"), 
        na.value = "grey80") + geom_vline(data = chromosome_boundaries, 
        aes(xintercept = boundary), color = "grey", linetype = "dashed", 
        alpha = 0.6) + labs(title = paste0("CNA ", samplename), 
        x = "Chromosome", y = "Coverage") + theme_minimal() + 
        theme(axis.text.x = element_text(angle = 45, hjust = 1), 
            axis.ticks.x = element_blank(), panel.grid = element_blank()) + 
        guides(color = "none") 
    # + scale_y_continuous(limits = c(ifelse(is.null(min_value), 
    #     min(offset$coverage_data$delta_weighted, na.rm = TRUE), 
    #     min_value), ifelse(is.null(max_value), max(offset$coverage_data$delta_weighted, 
    #     na.rm = TRUE), max_value))) + scale_x_continuous(breaks = chromosome_midpoints$midpoint, 
    #     labels = chromosome_midpoints$seqnames)
    if (return_data) {
        return(list(plot = p, coverage_data = offset$coverage_data, 
            variant_calls = offset$variant_calls))
    }
    else {
        return(p)
    }
}

```



```{r, include = F, eval=F}
library(pacbiowdlR)
a4573 <- read_json_file("/Volumes/furlan_s/grp/data/FurlanLab2025/lewings/pbWGS/A4573/pacbiowdlR/outputs.json", sub1 = "/fh/fast")
tc71 <- read_json_file("/Volumes/furlan_s/grp/data/FurlanLab2025/lewings/pbWGS/TC71/pacbiowdlR/outputs.json", sub1 = "/fh/fast")
tc32 <- read_json_file("/Volumes/furlan_s/grp/data/FurlanLab2025/lewings/pbWGS/TC32/pacbiowdlR/outputs.json", sub1 = "/fh/fast")

a4573$humanwgs_singleton.stat_mean_depth

chla10 <- read_json_file("/Volumes/furlan_s/grp/data/FurlanLab2025/lewings/pbWGS/CHLA10/pacbiowdlR/outputs.json", sub1 = "/fh/fast")
chla9 <- read_json_file("/Volumes/furlan_s/grp/data/FurlanLab2025/lewings/pbWGS/CHLA9/pacbiowdlR/outputs.json", sub1 = "/fh/fast")

chla9$humanwgs_singleton.stat_mean_depth
chla10$humanwgs_singleton.stat_mean_depth


CNA_plot(depth_bigwig_file  =   a4573$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   a4573$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "a4573", line_color = "black")

CNA_plot(depth_bigwig_file  =   tc71$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   tc71$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "TC71", line_color = "black")

CNA_plot(depth_bigwig_file  =   tc32$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   tc32$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "TC32", line_color = "black")


CNA_plot(depth_bigwig_file  =   chla10$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   chla10$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "CHLA10", line_color = "black")

CNA_plot(depth_bigwig_file  =   chla9$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   chla9$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "CHLA9", line_color = "black")

CNA_plot_highlight(depth_bigwig_file  =   chla10$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   chla10$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr9", highlight_genes = "CDKN2A",
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "CHLA10")

CNA_plot_highlight(depth_bigwig_file  =   chla9$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   chla9$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr16", gene_delta_threshold = 10, 
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "CHLA9")

CNA_plot_highlight(depth_bigwig_file  =   tc71$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   tc71$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr9", highlight_genes = "CDKN2A",
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "TC71")
```




```{r, include = F, eval=F}
library(pacbiowdlR)
EW1 <- read_json_file("/Volumes/furlan_s/sfurlan/250520_leuklong/pbWGS/LL2_EW1/pacbiowdlR/outputs.json")
EW1$humanwgs_singleton.stat_mean_depth
CNA_plot(depth_bigwig_file  =   EW1$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   EW1$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "EW1", line_color = "black")
CNA_plot_highlight(depth_bigwig_file  =   EW1$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   EW1$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr9", highlight_genes = "CDKN2A",
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "EW1")

S5 <- read_json_file("/Volumes/furlan_s/sfurlan/250520_leuklong/pbWGS/LL2_S5/pacbiowdlR/outputs.json")
S5$humanwgs_singleton.stat_mean_depth
CNA_plot(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   S5$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "S5", line_color = "black")

MAF_plot(maf_bigwig_file =  S5$humanwgs_singleton.cnv_maf_bw, downsample = .1, jitter_y = 0.01,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  chr_filter = "chr7", 
                  colors = chrom_palette, samplename = "S5")

MAF_plot(maf_bigwig_file =  S5$humanwgs_singleton.cnv_maf_bw, downsample = .1, jitter_y = 0.01,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  chr_filter = "chr9", 
                  colors = chrom_palette, samplename = "S5")

CNA_plot_highlight(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, downsample = .1,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", chr_filter = "chr7", line_color = "black",  highlight_genes = c( "IKZF1"),
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S5")

CNA_plot_highlight(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, downsample = .1,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black",  highlight_genes = c("CDKN2A", "PAX5", "IKZF1"),
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S5")


CNA_plot_highlight(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr9", highlight_genes = c("CDKN2A", "PAX5"),
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S5")

CNA_plot_highlight(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr8", highlight_genes = "MYC",
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S5")

CNA_plot_highlight(depth_bigwig_file  =   S5$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   S5$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr10", 
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S5")


S12 <- read_json_file("/Volumes/furlan_s/sfurlan/250520_leuklong/pbWGS/LL2_S12/pacbiowdlR/outputs.json")
S12$humanwgs_singleton.stat_mean_depth
CNA_plot(depth_bigwig_file  =   S12$humanwgs_singleton.cnv_depth_bw, trend_regions = "inside",
  variant_file       =   S12$humanwgs_singleton.cnv_vcf, 
  downsample         = 0.1,  method = "fit", min_value = -3, max_value = 3, colors = chrom_palette,
  samplename         = "S12", line_color = "black")
CNA_plot_highlight(depth_bigwig_file  =   S12$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   S12$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr9", highlight_genes = "CDKN2A",
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S12")

CNA_plot_highlight(depth_bigwig_file  =   S12$humanwgs_singleton.cnv_depth_bw, downsample = 1,
                  variant_file       =   S12$humanwgs_singleton.cnv_vcf, max_value = 3, min_value = -3,
                  method = "fit", line_color = "black", chr_filter = "chr15", 
                  colors = chrom_palette, txdb = TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene, 
                  org = org.Hs.eg.db::org.Hs.eg.db, samplename = "S12")

```
